Bullet Groups as a test of $\Lambda$CDM

### 2014-03-03 paper/ms.tex
rewriting

%\documentclass{emulateapj}
\documentclass{aastex}
\submitted{{\it Submitted for publication in ApJL}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}

@@

The configuration of this system is shown in  Figure
\ref{configuration}, where can be distinguish the host halo and
substructure for the a particular configuration in z$=0$ and the 
mass ranges and number of host halos and substructures 
are summary in the Table \ref{table1}. Of all the possible configurations that can be presented
in Figure \ref{configuration}, we are interested in estimate in the simulation the number 
of Bullet Groups that may be present in an Universe of 250 $h^{-1}$Mpc. For this we selected 
of the simulations all the substructures  
whose velocities indicate a movement out of the host halo. Each halo in this sample has a quantity
called $X_{off}$ that corresponds to the distance halo center (the minimum of the gravitational potential) to 
the center of mass normalized by the
virial radius ($R_{vir}$). Values of $X_{off}$
equal to zero indicate relaxed halos, while $X_{off}>0$ indicates the existence
of perturbed halos which can be considered candidates to be Bullet Groups and this ditribution is shown 
in a scatter plot in the Figure \ref{cos_theta1} and the distribution of $\nu_{circ,Halo}/\nu_{circ,Sub}$ 
is shown in  Figure \ref{cos_theta2}, both figures for differents z.

\begin{table}
\begin{center}
\begin{tabular}{ccccccc}\hline\hline
Sample       & Minimum Mass           & Maximum Mass          & \# Halos  & \# Halos  & \# Halos & \# Halos \\
             & M$_{\odot}$h$^{-1}$    & M$_{\odot}$h$^{-1}$   &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
Host Halo    & 0.35$\times{}10^{14}$  & 1.09$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\
Substructure & 0.38$\times{}10^{11}$  & 0.30$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\\hline
\end{tabular} 
\caption{Mass ranges for the two groups selected in this work in different redshifts.}
\label{table1}
\end{center}
\end{table}

\begin{figure*}
\begin{center}
\includegraphics[width=0.90\textwidth]{Figures_eps/Bullet_Group.eps}
\end{center}
\caption{Configuration for a host halo (dashed circle) and sub-structure (black circle) in the sample. } 
\label{configuration}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_4.eps}
\end{center}
\caption{Scatter plot for $X_{off}$ as function of the relation between velocities of substructures and the host halos and 
for different z. The top panel is represented to the sample with $\nu>700$ kms$^{-}1$ and down panel is represented 
for $\nu<700$ kms$^{-1}$} 
\label{cos_theta1}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_2.eps}
\end{center}
\caption{Distributions of $\nu_{circ,Halo}/\nu_{circ,Sub}$ for differents z. The left panel correpond to the sample 
with $\v>700$ kms$^{-1}$ and right panel correpond to the sample with $\nu<700$ kms$^{-1}$.} 
\label{cos_theta2}
\end{figure*}

@@

\begin{equation}
 \frac{\nu_{circ,sub}}{\nu_{circ,halo}}=0.5
\end{equation}

Figure \ref{newparameter} shows the scatter plot of the parameter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)$ vs the 
displacement ($d_{2d,(X,Y)}$) between the host halo and the substructure and for different redshifts. This parameter is 
consistent with the observations. The red star simbol in the Figure \ref{newparameter} is equal to 0.54 corresponding to 
the fraction in velocity dispersion in the line-of-sigth of the group SL2S SJ08544-0121 ($\sigma_{host,halo}=341^{+43}_{-109}$ kms$^{-1}$ and $\sigma_{substructure}=185^{+30}_{-62}$), reported by \citet{2013A&A...552A..80M}.
Based in the parameter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)>0.5$, we estimate the expected distribution of
displacements and this is shown in the Figure \ref{displacements} for the two groups classified in this work.

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_3.eps}
\end{center}
\caption{Scatter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)$
  vs $d_{2d,(X,Y)}$ for different redshifts. The  horizontal dashed
  line correpond to
  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.5$ and the
  red star simbol correspond to
  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.54$ for SL2S
  SJ08544-0121 in \citet{2013A&A...552A..80M}. The  four top panels
  are the sample with circular velocities $>700$ kms$^{-1}$ and the
  four down panels are the sample with  circular velocities between
  300 km s$^{-1}$ to 700 kms$^{-1}$.} 
\label{newparameter}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
\end{center}
\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements
  for the projection (X,Y). {\bf Left panel:} Sample with
  $\nu_{max}>700$ kms$^{-1}$  for different redshifts. The vertical
  dashed line, correspond to the separation between dark matter to
  dark matter estimate in this work as the double of separation
  between the collisional gas and dark matter of 124$\pm$20 kpc
  reported by \citet{Gastaldello} for the group SL2S J08544-0121.
  {\bf Right panel:} Sample with $300 $ kms$^{-1} <\nu_{max}<700 $
  kms$^{-1}$ for different redshifts.}  
\label{displacements}
\end{figure*}

@@

 \begin{equation}
  cos(\theta)=\frac{\vec{\nu{}}\cdotp{}\vec{r}}{\left\|\nu{}\right\| \left\|r\right\|}
 \end{equation}

where, $\vec{\nu{}}=\vec{\nu}_{sub}-\vec{\nu}_{halo}$ and $\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$, in the Figure \ref{cos_theta}
is shown the scatter plot of $cos(\theta{})$ vs $X_{off,new}=\frac{d_{2d,(X,Y)}}{R_{virial,halo}}=\frac{d_{real,(X,Y)}}{R_{virial,halo}}$.

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_1_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Scatter of $cos(\theta)$ vs $X_{off,new}$. The red dashed line correpond to the limit for $cos(\theta{})>0.5$,  
where the substructure is emerging from the host halo and  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cos_theta}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_3_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Cumulative distribution of $d_{real, (X,Y)}$ for $cos(\theta)>0.5$, $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cumulative_cos}
\end{figure*}

>>>>

\documentclass{emulateapj}
%\documentclass{aastex}
\submitted{{\it Submitted for publication in ApJL}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}

@@

The configuration of the BGs in the simulations is shown in Figure
\ref{configuration}. There we depict a host and its most massive
sub-halo from in a particular case found at z$=0$. The arrows show the
position and the velocity vectors sub-halo in a frame of reference
where the main halo is at rest; thus  $\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and
$\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$.  The angle between these two
vectors characterized by,
\begin{equation}
  \mu\equiv \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|v{}\right\| \left\|r\right\|}
 \end{equation} 
%
encodes the geometry of the collision, i.e. cases of $|\mu|\approx 1$
can be considered as head-on collisions while $|\mu|\approx 0$
describe a grazing trajectory.

The bullet-like encounter can be instantaneously described by
quantities the following quantities the circular velocity of the host
and the sub-halo, $V_{\rm c,host}$ and $V_{\rm c,  sub}$; the size of
the host halo $R_{\rm vir}$; the relative position and velocity of the
substructre, $\vec{v}$ and $\vec{r}$; and the angle between the
position and velocity $\mu$.

Using these quantities one can describe three main stages in a
Bullet-like collision. First, the sub-halo crosses the virial radius
of the host halo in a head-on fashion, $|\vec{r}|/R_{\rm vir}\approx
1$ and $\mu\approx<0.0$. Second, as the sub-halo crosses for the first
time the center of the host halo $|\vec{r}|/R_{\rm vir} <
1.0$ and $\mu>0.0$. Third, as the sub-halo reaches apogee and
comes back to the center of the halo $|\vec{r}|/R_{\rm vir} < 1.0$ and
$\mu<0.0$.

the 
mass ranges and number of host halos and substructures 
are summary in the Table \ref{table1}. Of all the possible configurations that can be presented
in Figure \ref{configuration}, we are interested in estimate in the simulation the number 
of Bullet Groups that may be present in an Universe of 250 $h^{-1}$Mpc. For this we selected 
of the simulations all the substructures  
whose velocities indicate a movement out of the host halo. Each halo in this sample has a quantity
called $X_{off}$ that corresponds to the distance halo center (the minimum of the gravitational potential) to 
the center of mass normalized by the
virial radius ($R_{vir}$). Values of $X_{off}$
equal to zero indicate relaxed halos, while $X_{off}>0$ indicates the existence
of perturbed halos which can be considered candidates to be Bullet Groups and this ditribution is shown 
in a scatter plot in the Figure \ref{cos_theta1} and the distribution of $\nu_{circ,Halo}/\nu_{circ,Sub}$ 
is shown in  Figure \ref{cos_theta2}, both figures for differents z.

\begin{table*}
\begin{center}
\begin{tabular}{ccccccc}\hline\hline
Sample       & Minimum $V_{\rm c}$         & Maximum $V_{\rm c}$          & \# Halos  & \# Halos  & \# Halos & \# Halos \\
             & \kms    & \kms  &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
Host   & 300\kms & XX &    400    &   362     &   310    &  192   \\ 
Sub-structure & 75\kms  & XX &    XX   &   XX     &   XX    &  XX   \\\hline
\end{tabular} 
\caption{Circular velocity ranges for the halos and subhalos at
  different redshifts.}  
\label{table1}
\end{center}
\end{table*}

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{Figures_eps/Bullet_Group.eps}
\end{center}
\caption{Configuration for a host halo (dashed circle) and
  sub-structure (black circle) in the sample.}  
\label{configuration}
\end{figure}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_4.eps}
\end{center}
\caption{Scatter plot for $X_{off}$ as function of the relation between velocities of substructures and the host halos and 
for different z. The top panel is represented to the sample with $v > 700$ \kms and down panel is represented 
for $v<700$ \kms} 
\label{cos_theta1}
\end{figure*}

\begin{figure*}
\begin{center}
%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_2.eps}
\end{center}
\caption{Integrated distributions of $|\vec{v}|/V_{\rm c,host}$ at all
  $z$. The left panel correponds to the sample with $V_{\rm c, host}>700$ \kms and
  right panel correpond to the sample with $V_{\rm c,host}<700\kms$.} 
\label{cos_theta2}
\end{figure*}

@@

\begin{equation}
 \frac{v_{circ,sub}}{v_{circ,halo}}=0.5
\end{equation}

Figure \ref{newparameter} shows the scatter plot of the parameter $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)$ vs the 
displacement ($d_{2d,(X,Y)}$) between the host halo and the substructure and for different redshifts. This parameter is 
consistent with the observations. The red star simbol in the Figure \ref{newparameter} is equal to 0.54 corresponding to 
the fraction in velocity dispersion in the line-of-sigth of the group SL2S SJ08544-0121 ($\sigma_{host,halo}=341^{+43}_{-109}$ kms$^{-1}$ and $\sigma_{substructure}=185^{+30}_{-62}$), reported by \citet{2013A&A...552A..80M}.
Based in the parameter $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)>0.5$, we estimate the expected distribution of
displacements and this is shown in the Figure \ref{displacements} for the two groups classified in this work.

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_3.eps}
\end{center}
\caption{Scatter $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)$
  vs $d_{2d,(X,Y)}$ for different redshifts. The  horizontal dashed
  line correpond to
  $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)=0.5$ and the
  red star simbol correspond to
  $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)=0.54$ for SL2S
  SJ08544-0121 in \citet{2013A&A...552A..80M}. The  four top panels
  are the sample with circular velocities $>700$ kms$^{-1}$ and the
  four down panels are the sample with  circular velocities between
  300 km s$^{-1}$ to 700 kms$^{-1}$.} 
\label{newparameter}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
\end{center}
\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements
  for the projection (X,Y). {\bf Left panel:} Sample with
  $v_{max}>700$ kms$^{-1}$  for different redshifts. The vertical
  dashed line, correspond to the separation between dark matter to
  dark matter estimate in this work as the double of separation
  between the collisional gas and dark matter of 124$\pm$20 kpc
  reported by \citet{Gastaldello} for the group SL2S J08544-0121.
  {\bf Right panel:} Sample with $300 $ kms$^{-1} <v_{max}<700 $
  kms$^{-1}$ for different redshifts.}  
\label{displacements}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_1_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Scatter of $cos(\theta)$ vs $X_{off,new}$. The red dashed line correpond to the limit for $cos(\theta{})>0.5$,  
where the substructure is emerging from the host halo and  $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cos_theta}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_3_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Cumulative distribution of $d_{real, (X,Y)}$ for $cos(\theta)>0.5$, $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cumulative_cos}
\end{figure*}
